---
title: 'Seattle University: Center for Community Engagement'
author: 'Prepared by: James Lamar Foster'
subtitle: Senior Data and Evaluation Analyst Interview
output:
  html_document:
    df_print: paged
  word_document:
    reference_docx: SeattleU_Template.docx
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#clear memory
rm(list = ls())
#penalize excessive significant figures
options(digits = 3)
#preventing scientific notation
options(scipen = 10)

#packages used in this analysis, will install packages if not installed
if(!require(knitr)){
    install.packages("knitr", dependencies = TRUE)
    library(knitr)
}
if(!require(tidyverse)){
    install.packages("tidyverse", dependencies = TRUE)
    library(tidyverse)
}
if(!require(haven)){
    install.packages("haven", dependencies = TRUE)
    library(haven)
}
if(!require(janitor)){
    install.packages("janitor", dependencies = TRUE)
    library(janitor)
}

if(!require(ggthemes)){
    install.packages("ggthemes", dependencies = TRUE)
    library(ggthemes)
}

if(!require(readxl)){
    install.packages("readxl", dependencies = TRUE)
    library(readxl)
}

library(RColorBrewer)
library(ggalt)
library(ggrepel)
library(kableExtra)
```

```{r set_knitr_chunk_options, echo=FALSE, message=FALSE}
#set global output chunk options
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, collapse=FALSE, highlight= FALSE, results='asis', fig.height = 4, fig.width = 7,  fig.align = "left")
```

```{r, message = F, warning=FALSE}
# Import Data
data <- read_xlsx("interview_data.xlsx")

#setting theme and centering the titles for ggplots
theme_set(theme_classic())
```

```{r}
# A little bit of cleaning

## Remove empty columns 
data <- clean_names(data) %>% 
  remove_empty(which = c("rows", "cols"), quiet = TRUE) 

##Rename columns 
data <- data %>% 
rename(
 latinx =  ethnicity_desc_p,
 race = race_desc_p,
 homeless = is_homeless, 
 school = school_name2010,
 gpa = gpa2014, 
 bilingual = bilg2014,
 fall_math = x2013fall_math_rit,
 winter_math = x2014wtr_math_rit,
 spring_math = x2014spr_math_rit,
 fall_reading = x2013fall_read_rit,
 winter_reading = x2014wtr_read_rit,
 spring_reading = x2014spr_read_rit,
 suyi = suyi_focus_students
 )

#Turn some character values to numbers 
data$latinx <- if_else(data$latinx == "Hispanic/Latino", 1, 0)
data$sex <- recode(data$sex, "M" = "Male", "F" = "Female")
data$homeless <- recode(data$homeless, "N" = 0, "Y" = 1)
data$sped <- recode(data$sped, "N" = 0, "Y" = 1)
data$bilingual <- recode(data$bilingual, "N" = 0, "Y" = 1)
data$suyi <- recode(data$suyi, "1" = "SUYI-Focus", "0" = "SUYI")

# Growth Index for math and reading 
data <- data %>% 
  mutate(math_growth = spring_math - fall_math ) %>% 
  mutate(reading_growth = spring_reading - fall_reading) 

data <- data %>% hablar::retype() 

# Treat some variables as factors 
data$suyi <- as.factor(data$suyi)
data$sped <- as.factor(data$sped)
data$race <- as.factor(data$race)
data$school <- as.factor(data$school)

# Turn NAs in home language variable to English 
#Turn NAs to zero for Race and Ethnicity Columns
data <- data %>%
  mutate_at(vars(home_language, primary_language), ~replace_na(., "English"))


#Make dataset of only variables used for analysis 
df <- data %>% select(-c(suyi_zone, status2014, withdraw_date, proj_grad_year))

#Create "Grade Level" column 
df <- df %>% 
mutate(grade_level =
         case_when(grade %in% c("1", "2", "3", "4", "5", "K") ~ "elementary",
                   grade %in% c("6", "7", "8")  ~ "middle",
                   grade %in% c("9", "10", "11", "12") ~ "high school"))

#Make grade_level a factor
df$grade_level <- factor(df$grade_level, 
                         levels = c("elementary", "middle", "high school"), 
                         labels = c("elementary", "middle", "high school"))

df_long <- pivot_longer(df, cols = fall_math:spring_reading) %>% 
  separate(name, c("semester", "subject"), sep = "_") %>% 
  rename(rit_score = value) 


#Make elementary, middle, and hs data frames 
elem <- df %>% filter(grade_level == "elementary")
middle <- df %>% filter(grade_level == "middle")
hs <- df %>% filter(grade_level == "high school")

#Make semester a factor
df_long$semester <- factor(df_long$semester, 
                         levels = c("fall", "winter", "spring"), 
                         labels = c("fall", "winter", "spring"))


```

```{r}
#Create smaller data frame for dumbbell viz

## Summarize Mean by School
mean_math <- df %>% 
  group_by(school, grade_level) %>% 
  summarise(mean_fall_math = mean(fall_math, na.rm = T),
            mean_spring_math = mean(spring_math, na.rm = T))

mean_read <- df %>% 
  group_by(school,grade_level) %>% 
  summarise(mean_fall_reading = mean(fall_reading, na.rm = T),
            mean_spring_reading = mean(spring_reading, na.rm = T))

## Turn summaries into a dataframe
mean_math <- as.data.frame(mean_math)
mean_read <- as.data.frame(mean_read)

## Create a Mean difference column 
mean_math <- mean_math %>% 
  mutate(mean_math_diff = round(mean_spring_math - mean_fall_math,2)) 

mean_read <- mean_read %>% 
  mutate(mean_reading_diff = round(mean_spring_reading - mean_fall_reading,2)) 
```
 
```{r}
# Create Mean_Read and Mean_Math datasets for each grade level 

## Math
elem_mean_math <- mean_math %>% filter(grade_level == "elementary") %>% arrange(desc(mean_math_diff))
middle_mean_math <- mean_math %>% filter(grade_level == "middle") %>% arrange(desc(mean_math_diff))
hs_mean_math <- mean_math %>% filter(grade_level == "high school") %>% arrange(desc(mean_math_diff))


## Reading 
elem_mean_reading <- mean_read %>% filter(grade_level == "elementary") %>% arrange(desc(mean_reading_diff))
middle_mean_reading <- mean_read %>% filter(grade_level == "middle") %>% arrange(desc(mean_reading_diff))
hs_mean_reading <- mean_read %>% filter(grade_level == "high school") %>% arrange(desc(mean_reading_diff))
```
 
```{r}
# Order School variable by mean reading difference variable

## Reading
elem_mean_reading$school <- fct_reorder(elem_mean_reading$school, elem_mean_reading$mean_reading_diff, max)

middle_mean_reading$school <- fct_reorder(middle_mean_reading$school, middle_mean_reading$mean_reading_diff, max)

hs_mean_reading$school <- fct_reorder(hs_mean_reading$school, hs_mean_reading$mean_reading_diff, max)


## Math
elem_mean_math$school <- fct_reorder(elem_mean_math$school, elem_mean_math$mean_math_diff, max)

middle_mean_math$school <- fct_reorder(middle_mean_math$school, middle_mean_math$mean_math_diff, max)

hs_mean_math$school <- fct_reorder(hs_mean_math$school, hs_mean_math$mean_math_diff, max)
```

---

# Youth Initiative Zone Schools and Students

```{r}
table <- data %>%
  group_by(School = school) %>%
  summarise("Total" = n()) %>%
  arrange(desc(Total)) %>% 
  adorn_totals("row") %>% 
  adorn_percentages(denominator = "col") %>% 
  adorn_pct_formatting() %>%
  adorn_ns() 


kable(table, caption= "Total Number of Students in the Seattle University Youth Initiative Zone", col.names = c("School Name", "Percent (Total)")) %>% kable_styling(full_width = T, bootstrap_options = c("striped", "responsive"), position = "left", fixed_thead = T)



table <- elem %>%
  group_by(School = school) %>%
  summarise("Total" = n()) %>%
  arrange(desc(Total)) %>% 
  adorn_totals("row") %>% 
  adorn_percentages(denominator = "col") %>% 
  adorn_pct_formatting() %>%
  adorn_ns() 


kable(table, caption= "Elementary Schools (K-5)", col.names = c("School Name", "Percent (Total)")) %>% kable_styling(full_width = T, bootstrap_options = c("striped", "responsive"), position = "left", fixed_thead = T)


table <- middle %>%
  group_by(School = school) %>%
  summarise("Total" = n()) %>%
  arrange(desc(Total)) %>% 
  adorn_totals("row") %>% 
  adorn_percentages(denominator = "col") %>% 
  adorn_pct_formatting() %>%
  adorn_ns() 


kable(table, caption= "Middle Schools (6-8)", col.names = c("School Name", "Percent (Total)")) %>% kable_styling(full_width = T, bootstrap_options = c("striped", "responsive"), position = "left", fixed_thead = T)

table <- hs %>%
  group_by(School = school) %>%
  summarise("Total" = n()) %>%
  arrange(desc(Total)) %>% 
  adorn_totals("row") %>% 
  adorn_percentages(denominator = "col") %>% 
  adorn_pct_formatting() %>%
  adorn_ns() 


kable(table, caption= "High Schools (9-12)", col.names = c("School Name", "Percent (Total)")) %>% kable_styling(full_width = T, bootstrap_options = c("striped", "responsive"), position = "left", fixed_thead = T)


data %>%
   group_by(school) %>%
  summarise("Total" = n()) %>% 
  ggplot(aes(school, Total,group= school)) +
  geom_col(aes(x= reorder(school, Total)), fill = "#AA0000") +
  scale_y_continuous(breaks = c(0,25,50,75,100,125,150, 175)) +
  labs(x = "School", 
       y = "Number of Students") + coord_flip() + theme(legend.position = "none")
```

# Youth Initiative Zone Student Demographics 

```{r}
# Student's Sex
table <- data %>%
  group_by(suyi) %>% 
   count("Sex" = sex ) %>%
   adorn_percentages(denominator = "col") %>% 
  adorn_pct_formatting() %>%
  adorn_ns()

kable(table, caption = "Student's Sex", col.names = c("Group","Sex", "Percent (Total)"))%>% kable_styling(full_width = T, bootstrap_options = c("striped", "responsive"), position = "left", fixed_thead = T) 

data %>% 
ggplot(aes(x= reorder(sex, primary_language,function(x)length(x)), fill= suyi)) + geom_bar(position = "dodge") + scale_fill_manual(values=c("black","#AA0000", name="Group")) + coord_flip() + labs(x= "Sex", fill = "Group")
```

```{r}
# Student's Race
table <- data %>%
   count("Racial Identity" = race, sort = T ) %>%
   adorn_percentages(denominator = "col") %>% 
  adorn_pct_formatting() %>%
  adorn_ns()

kable(table, caption = "Student's Racial Identity", col.names = c("Racial Identity", "Percent (Total)")) %>% kable_styling(full_width = T, bootstrap_options = c("striped", "responsive"), position = "left", fixed_thead = T)

data %>% 
ggplot(aes(x= reorder(race, primary_language,function(x)length(x)))) + geom_bar(position = "dodge", fill = "black") + coord_flip() + labs(x= "Racial Identity")
```

```{r}
# Student's Primary Language
table <- data %>%
   filter(primary_language != "English") %>% 
   count("Primary Language" = primary_language, sort = T) %>%
  filter(n >= 8) %>% 
   adorn_percentages(denominator = "col") %>% 
  adorn_pct_formatting() %>%
  adorn_ns()

kable(table, caption = "Student's Primary Language", col.names = c("Primary Language", "Percent (Total)")) %>% kable_styling(full_width = T, bootstrap_options = c("striped", "responsive"), position = "left", fixed_thead = T)

data %>% 
  filter(primary_language != "English") %>% 
ggplot(aes(x= reorder(primary_language, primary_language,function(x)length(x)))) + geom_bar(position = "dodge", fill = "#AA0000") + scale_fill_manual(values=c("black","#AA0000", name="Group")) + coord_flip() + labs(x= "Primary Language")
```

```{r}
# Number of Bilingual Student 
table <- data %>% 
  summarise(
    "n" = sum(bilingual),
    "Percent Bilingual" = round((n/n())*100,2))

kable(table, caption = "Bilingual Students", col.names = c("Total", "Percent"), full_width = F) %>% kable_styling(full_width = F, bootstrap_options = "responsive", position = "left", fixed_thead = T)

library(waffle)

bilingual <- c(34, 66)
waffle(bilingual, rows=5, size=0.5, 
       colors = c("#AA0000", "black"),
       title="Percent of Bilingual Students", 
       xlab="1 square = 1 Percent")

```

```{r}
# Number of Students Experiencing Homelessness
table <- data %>% 
  summarise(
    "n" = sum(as.numeric(homeless)),
    "Percent Homeless" = round((n/n())*100,2),
  )
kable(table, caption = "Students Experiencing Homelessness", col.names = c("Total", "Percent"), full_width = F) %>% kable_styling(full_width = F, bootstrap_options = "responsive", position = "left", fixed_thead = T)

data %>% 
  group_by(suyi) %>% 
  summarise(y = round((sum(homeless)/n())*100,2)) %>% 
  ggplot(aes(suyi,y, fill = suyi, fill = suyi)) + scale_fill_manual(values=c("black","#AA0000")) + labs(x = "", y = "Percent", fill= "Group") + scale_y_continuous(limits=c(0, 100)) + geom_col() + coord_flip()
```

---

# Student Attendance 
A student is considered "chronically absent" when they miss 15 or more days of instruction in one academic school year. Chronic absenteeism can lead to student's missing important instructional time, ultimately causing students to fall behind in their academics. Furthermore, when students miss school they also miss important social interaction times that develop their interpersonal skills. 

According to this analysis, students in the Youth Initative Zone miss an average of 12 days of instruction. High School students make up for the majority of the days missed, with New Futures Alternative, Cascade High School, and Olympic High School having the highest median of absenteeism. On the other hand, elementary school students account for the least amount of absences. Horizon, Franklin, and Valley Elementary have the lowest amount of students missing school. 

```{r}
table <- data %>% 
  summarise(
    "Min" = min(days_absent),
    "Median" = median(days_absent),
    "Mean" = mean(days_absent),
    "Max" = max(days_absent))

kable(table, caption = "School Absenteeism", full_width = F) %>% kable_styling(full_width = F, bootstrap_options = "responsive", position = "left", fixed_thead = T)

data %>% 
  ggplot(aes(reorder(school, days_absent, FUN = median), days_absent)) + geom_boxplot(fill = "grey90") + coord_flip() + labs(x = "School", y = "Days Absent")

```

```{r}
#Elementary Attendance 

table <- elem %>% 
  group_by("School" = school) %>%
  summarise(
    "Min" = min(days_absent),
    "Median" = median(days_absent),
    "Mean" = mean(days_absent),
    "Max" = max(days_absent))%>% 
  arrange(desc(Median))

kable(table, caption = "Elementary School Absenteeism") %>% kable_styling(full_width = T, bootstrap_options = c("striped", "responsive"), position = "left", fixed_thead = T)

elem %>% 
  ggplot(aes(reorder(school, days_absent, FUN = median), days_absent)) + geom_boxplot(fill = "#4F95DB") + coord_flip() + labs(x = "School", y = "Days Absent")
```

```{r}
#Middle School Attendance 

table <- middle %>% 
  group_by("School" = school) %>%
  summarise(
    "Min" = min(days_absent),
    "Median" = median(days_absent),
    "Mean" = mean(days_absent),
    "Max" = max(days_absent))%>% 
  arrange(desc(Median))

kable(table, caption = "Middle School Absenteeism") %>% kable_styling(full_width = T, bootstrap_options = c("striped", "responsive"), position = "left", fixed_thead = T)

middle %>% 
  ggplot(aes(reorder(school, days_absent, FUN = median), days_absent)) + geom_boxplot(fill = "#DBA14F") + coord_flip() + labs(x = "School", y = "Days Absent")
```

```{r}
#High School Attendance 

table <- hs %>% 
  group_by("School" = school) %>%
  summarise(
    "Min" = min(days_absent),
    "Median" = median(days_absent),
    "Mean" = mean(days_absent),
    "Max" = max(days_absent)) %>% 
  arrange(desc(Median))

kable(table, caption = "High School Absenteeism") %>% kable_styling(full_width = T, bootstrap_options = c("striped", "responsive"), position = "left", fixed_thead = T)

hs %>% 
  ggplot(aes(reorder(school, days_absent, FUN = median), days_absent)) + geom_boxplot(fill = "#2ca25f") + coord_flip() + labs(x = "School", y = "Days Absent")
```

---

# RIT Scores 
```{r, warning=F}
#Average Math and Reading RIT by Grade Level 
df_long %>% 
  group_by(subject, semester, grade_level) %>% 
  summarise(y= mean(rit_score, na.rm = T)) %>% 
  ggplot(aes(semester, y, color = subject, group = subject)) + scale_color_manual(values=c("black", "#AA0000")) + labs(title= "Average Math and Reading RIT Score by Grade Level" ,x = "Semester", y = "Average Score") + geom_point() + geom_line() + facet_wrap(~grade_level)
```

```{r, warning=F}
#Average RIT Score by Sex
df_long %>% 
  group_by(subject, semester, sex) %>% 
  summarise(y= mean(rit_score, na.rm = T)) %>% 
  ggplot(aes(semester, y, color = subject, group = subject)) + scale_color_manual(values=c("black", "#AA0000")) + labs(title= "Average Math and Reading RIT Score by Grade Level" ,x = "Semester", y = "Average Score") + geom_point() + geom_line() + facet_wrap(~sex)
```

```{r, warning=F}
#Average RIT Score by Race
df_long %>% 
  group_by(subject, semester, race) %>% 
  summarise(y= mean(rit_score, na.rm = T)) %>% 
  ggplot(aes(semester, y, color = subject, group = subject)) + scale_color_manual(values=c("black", "#AA0000")) + labs(title= "Average Math and Reading RIT Score by Race" ,x = "Semester", y = "Average Score") + geom_point() + geom_line() + facet_wrap(~race)
```

```{r, eval= FALSE}
#RIT Math Growth 
elem %>% 
  filter(!is.na(math_growth)) %>% 
  ggplot(aes(reorder(school, math_growth, FUN = median), math_growth, fill = school)) + geom_boxplot()  + labs(x = "School", y = "Math Growth") + coord_flip() + scale_fill_brewer(palette="RdBu")
 
```
 
---

# RIT Growth Plots

## Reading 

### Elementary Schools
```{r, warning = FALSE}
# Elementary Reading Dumbbell Plot 
ggplot(elem_mean_reading, aes(x=mean_fall_reading, xend=mean_spring_reading, y=school)) + geom_segment(aes(x=150, 
                         xend=250, 
                         y=school, 
                         yend=school), 
                     color="grey90", size=1)+
        geom_dumbbell(color="black", 
                      size_x=3.5, 
                      size_xend = 3.5,
                      colour_x="black", 
                      colour_xend = "#AA0000")+
        labs(x="Reading Score", y="School", 
             title="Elementary Fall to Spring Average RIT Reading Scores", 
             caption="2014 School year") +
    geom_text(data=filter(elem_mean_reading, school == "Valley Elementary"), aes(x=mean_fall_reading, y=school, label="Fall"),
          color="black", size=2.75, vjust=-2.5, position = position_dodge(width = 2)) +
geom_text(data=filter(elem_mean_reading, school == "Valley Elementary"), color="#AA0000", size=2.75, vjust=-2.5,
          aes(x=mean_spring_reading, y=school, label="Spring"), position = position_dodge(width = 2)) +
  geom_text(data=elem_mean_reading, aes(x=mean_fall_reading, y=school, label=round(mean_fall_reading,2)),
          color="black", size=2.75, vjust=2.5, position = position_dodge(width = 2)) +
geom_text(data=elem_mean_reading, color="black", size=2.75, vjust=2.5,
          aes(x=mean_spring_reading, y=school, label=round(mean_spring_reading,2)), position = position_dodge(width = 2)) +
  geom_rect(data=elem_mean_reading, aes(xmin=230, xmax=250, ymin=-Inf, ymax=Inf), fill="grey90") +
geom_text(data=elem_mean_reading, aes(label=paste0(round(mean_reading_diff,2)), y=school, x=240), fontface="bold", size=3) +
geom_text(data= filter(elem_mean_reading, school == "Valley Elementary"), 
            aes(x=240, y=school, label="Grwoth Index"),
            color="black", size=3.1, vjust=-3, fontface="bold") + scale_x_continuous(expand=c(0,0), limits=c(150, 250)) + scale_y_discrete(expand=c(0.2,0))
```
 
### Middle Schools
```{r}
#Middle Reading Dumbbell Plot 
ggplot(middle_mean_reading, aes(x=mean_fall_reading, xend=mean_spring_reading, y=school)) + geom_segment(aes(x=150, 
                         xend=250, 
                         y=school, 
                         yend=school), 
                     color="grey90", size=1)+
        geom_dumbbell(color="black", 
                      size_x=3.5, 
                      size_xend = 3.5,
                      colour_x="black", 
                      colour_xend = "#AA0000")+
        labs(x="Reading Score", y="School", 
             title="Middle School Fall to Spring Average RIT Reading Scores", 
             caption="2014 School year") +
    geom_text(data=filter(middle_mean_reading, school == "Sound View Middle School"), aes(x=mean_fall_reading, y=school, label="Fall"),
          color="black", size=2.75, vjust=-2.5, position = position_dodge(width = .5)) +
geom_text(data=filter(middle_mean_reading, school == "Sound View Middle School"), color="#AA0000", size=2.75, vjust=-2.5,
          aes(x=mean_spring_reading, y=school, label="Spring"), position = position_dodge(width = 2)) +
  geom_text_repel(data=middle_mean_reading, aes(x=mean_fall_reading, y=school, label=round(mean_fall_reading,2)),
          color="black", size=2.75, vjust=2.5, position = position_dodge(width = .5)) +
geom_text_repel(data=middle_mean_reading, color="black", size=2.75, vjust=-1,
          aes(x=mean_spring_reading, y=school, label=round(mean_spring_reading,2))) +
  geom_rect(data=middle_mean_reading, aes(xmin=230, xmax=250, ymin=-Inf, ymax=Inf), fill="grey90") +
geom_text(data=middle_mean_reading, aes(label=paste0(round(mean_reading_diff,2)), y=school, x=240), fontface="bold", size=3) +
geom_text(data= filter(middle_mean_reading, school == "Sound View Middle School"), 
            aes(x=240, y=school, label="Grwoth Index"),
            color="black", size=3.1, vjust=-3, fontface="bold") + scale_x_continuous(expand=c(0,0), limits=c(150, 250)) + scale_y_discrete(expand=c(0.2,0))
```
 
### High Schools 
```{r}
#High School Reading Dumbbell Plot 
ggplot(hs_mean_reading, aes(x=mean_fall_reading, xend=mean_spring_reading, y=school)) + geom_segment(aes(x=150, 
                         xend=250, 
                         y=school, 
                         yend=school), 
                     color="grey90", size=1)+
        geom_dumbbell(color="black", 
                      size_x=3.5, 
                      size_xend = 3.5,
                      colour_x="black", 
                      colour_xend = "#AA0000")+
        labs(x="Reading Score", y="School", 
             title="High School Fall to Spring Average RIT Reading Scores", 
             caption="2014 School year") +
    geom_text(data=filter(hs_mean_reading, school == "Olympic High School"), aes(x=mean_fall_reading, y=school, label="Fall"),
          color="black", size=2.75, vjust=-2.5, position = position_dodge(width = 2)) +
geom_text(data=filter(hs_mean_reading, school == "Olympic High School"), color="#AA0000", size=2.75, vjust=-2.5,
          aes(x=mean_spring_reading, y=school, label="Spring"), position = position_dodge(width = 2)) +
  geom_text(data=hs_mean_reading, aes(x=mean_fall_reading, y=school, label=round(mean_fall_reading,2)),
          color="black", size=2.75, vjust=2.5, position = position_dodge(width=.5)) +
geom_text(data=hs_mean_reading, color="black", size=2.75, vjust=-1,
          aes(x=mean_spring_reading, y=school, label=round(mean_spring_reading,2)), position = position_dodge(width=1)) +
  geom_rect(data=hs_mean_reading, aes(xmin=230, xmax=250, ymin=-Inf, ymax=Inf), fill="grey90") +
geom_text(data=hs_mean_reading, aes(label=paste0(round(mean_reading_diff,2)), y=school, x=240), fontface="bold", size=3) +
geom_text(data= filter(hs_mean_reading, school == "Olympic High School"), 
            aes(x=240, y=school, label="Grwoth Index"),
            color="black", size=3.1, vjust=-3, fontface="bold") + scale_x_continuous(expand=c(0,0), limits=c(150, 250)) + scale_y_discrete(expand=c(0.2,0))
```
 
 
 
 
-Make tables to accompany each graph made 
- Write up a summary of the findings 


