---
title: 'Seattle University: Center for Community Engagement'
author: 'Prepared by: James Lamar Foster'
subtitle: Senior Data and Evaluation Analyst Interview
output:
  html_document:
    df_print: paged
  word_document:
    reference_docx: SeattleU_Template.docx
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#clear memory
rm(list = ls())
#penalize excessive significant figures
options(digits = 3)
#preventing scientific notation
options(scipen = 10)

#packages used in this analysis, will install packages if not installed
if(!require(knitr)){
    install.packages("knitr", dependencies = TRUE)
    library(knitr)
}
if(!require(tidyverse)){
    install.packages("tidyverse", dependencies = TRUE)
    library(tidyverse)
}
if(!require(haven)){
    install.packages("haven", dependencies = TRUE)
    library(haven)
}
if(!require(janitor)){
    install.packages("janitor", dependencies = TRUE)
    library(janitor)
}

if(!require(ggthemes)){
    install.packages("ggthemes", dependencies = TRUE)
    library(ggthemes)
}

if(!require(readxl)){
    install.packages("readxl", dependencies = TRUE)
    library(readxl)
}

library(RColorBrewer)
library(ggalt)
```

```{r set_knitr_chunk_options, echo=FALSE, message=FALSE}
#set global output chunk options
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, collapse=FALSE, highlight= FALSE, results='asis', fig.height = 4, fig.width = 7,  fig.align = "left")
```

```{r, message = F, warning=FALSE}
# Import Data
data <- read_xlsx("interview_data.xlsx")

#setting theme and centering the titles for ggplots
theme_set(theme_classic())
```

```{r}
#R function to add significance stars to a p-value
star <- function(pval) {
  if (pval <= 0.001) {
    return("p < .001")
  }
  if (pval <= 0.01) {
    return(" p < .01")
  }		
  if (pval <= 0.05) {
    return(" p < .05")
  }
  #if (pval <= 0.1) {
  #  return("p < .1")
  #}
  else {return("n.s.")
  }
}
```

```{r}
# A little bit of cleaning

## Remove empty columns 
data <- clean_names(data) %>% 
  remove_empty(which = c("rows", "cols"), quiet = TRUE) 

##Rename columns 
data <- data %>% 
rename(
 latinx =  ethnicity_desc_p,
 race = race_desc_p,
 homeless = is_homeless, 
 school = school_name2010,
 gpa = gpa2014, 
 bilingual = bilg2014,
 fall_math = x2013fall_math_rit,
 winter_math = x2014wtr_math_rit,
 spring_math = x2014spr_math_rit,
 fall_reading = x2013fall_read_rit,
 winter_reading = x2014wtr_read_rit,
 spring_reading = x2014spr_read_rit,
 suyi = suyi_focus_students
 )

#Turn some character values to numbers 
data$latinx <- if_else(data$latinx == "Hispanic/Latino", 1, 0)
data$sex <- recode(data$sex, "M" = "Male", "F" = "Female")
data$homeless <- recode(data$homeless, "N" = 0, "Y" = 1)
data$sped <- recode(data$sped, "N" = 0, "Y" = 1)
data$bilingual <- recode(data$bilingual, "N" = 0, "Y" = 1)
data$suyi <- recode(data$suyi, "1" = "SUYI-Focus", "0" = "SUYI")

# Growth Index for math and reading 
data <- data %>% 
  mutate(math_growth = spring_math - fall_math ) %>% 
  mutate(reading_growth = spring_reading - fall_reading) 

data <- data %>% hablar::retype() 

# Treat some variables as factors 
data$suyi <- as.factor(data$suyi)
data$sped <- as.factor(data$sped)
data$race <- as.factor(data$race)
data$school <- as.factor(data$school)

# Turn NAs in home language variable to English 
#Turn NAs to zero for Race and Ethnicity Columns
data <- data %>%
  mutate_at(vars(home_language, primary_language), ~replace_na(., "English"))


#Make dataset of only variables used for analysis 
df <- data %>% select(-c(suyi_zone, status2014, withdraw_date, proj_grad_year))

#Create "Grade Level" column 
df <- df %>% 
mutate(grade_level =
         case_when(grade %in% c("1", "2", "3", "4", "5", "K") ~ "elementary",
                   grade %in% c("6", "7", "8")  ~ "middle",
                   grade %in% c("9", "10", "11", "12") ~ "high school"))

#Make grade_level a factor
df$grade_level <- factor(df$grade_level, 
                         levels = c("elementary", "middle", "high school"), 
                         labels = c("elementary", "middle", "high school"))

df_long <- pivot_longer(df, cols = fall_math:spring_reading) %>% 
  separate(name, c("semester", "subject"), sep = "_") %>% 
  rename(rit_score = value) 


#Make elementary, middle, and hs data frames 
elem <- df %>% filter(grade_level == "elementary")
middle <- df %>% filter(grade_level == "middle")
hs <- df %>% filter(grade_level == "high school")

#Make semester a factor
df_long$semester <- factor(df_long$semester, 
                         levels = c("fall", "winter", "spring"), 
                         labels = c("fall", "winter", "spring"))


```

---

# Youth Initiative Zone Schools and Students

```{r}
table <- data %>%
  group_by(School = school, Group = suyi) %>%
  summarise("Total" = n()) %>%
  adorn_totals("row") %>% 
  adorn_percentages(denominator = "col") %>% 
  adorn_pct_formatting() %>%
  adorn_ns()


kable(table, caption = "Respondents by School", col.names = c("School Name", "Group", "Percent (Total)")) 


data %>%
   group_by(School = school, SUYI = suyi) %>%
  summarise("Total" = n()) %>% 
ggplot(aes(School, Total)) +
  geom_col(aes(fill = SUYI, x= reorder(School, Total)), position = "dodge") +
  scale_y_continuous(breaks = c(0,25,50,75,100,125,150)) +
  labs(x = "School", 
       y = "Number of Respondents") +
  scale_fill_manual(values=c("black","#AA0000", name="Group")) + coord_flip()
```

# Youth Initiative Zone Student Demographics 

```{r}
# Student's Sex
table <- data %>%
  group_by(suyi) %>% 
   count("Sex" = sex ) %>%
   adorn_percentages(denominator = "col") %>% 
  adorn_pct_formatting() %>%
  adorn_ns()

kable(table, caption = "Student's Sex", col.names = c("Group","Sex", "Percent (Total)")) 

data %>% 
ggplot(aes(x= reorder(sex, primary_language,function(x)length(x)), fill= suyi)) + geom_bar(position = "dodge") + scale_fill_manual(values=c("black","#AA0000", name="Group")) + coord_flip() + labs(x= "Sex")
```

```{r}
# Student's Race
table <- data %>%
  group_by(suyi) %>% 
   count("Racial Identity" = race ) %>%
   adorn_percentages(denominator = "col") %>% 
  adorn_pct_formatting() %>%
  adorn_ns()

kable(table, caption = "Student's Primary Language", col.names = c("Group","Racial Identity", "Percent (Total)")) 

data %>% 
ggplot(aes(x= reorder(race, primary_language,function(x)length(x)), fill= suyi)) + geom_bar(position = "dodge") + scale_fill_manual(values=c("black","#AA0000", name="Group")) + coord_flip() + labs(x= "Racial Identity")
```

```{r}
# Student's Primary Language
table <- data %>%
  group_by(suyi) %>% 
   filter(primary_language != "English") %>% 
   count("Primary Language" = primary_language ) %>%
  filter(n >= 8) %>% 
   adorn_percentages(denominator = "col") %>% 
  adorn_pct_formatting() %>%
  adorn_ns()

kable(table, caption = "Student's Primary Language", col.names = c("Group","Primary Language", "Percent (Total)")) 

data %>% 
  filter(primary_language != "English") %>% 
ggplot(aes(x= reorder(primary_language, primary_language,function(x)length(x)), fill= suyi)) + geom_bar(position = "dodge") + scale_fill_manual(values=c("black","#AA0000", name="Group")) + coord_flip() + labs(x= "Primary Language")
```

```{r}
# Number of Bilingual Student 
table <- data %>% 
  group_by("Group" = suyi) %>%
  summarise(
    "n" = sum(as.numeric(bilingual)),
    "Percent Bilingual" = round((n/n())*100,2))

kable(table, caption = "Bilingual Students", col.names = c("Group", "Total", "Percent"))

data %>% 
  group_by(suyi) %>% 
  summarise(y = round((sum(bilingual)/n())*100,2)) %>% 
  ggplot(aes(suyi,y, fill = suyi, fill = suyi)) + scale_fill_manual(values=c("black","#AA0000")) + labs(x = "", y = "Percent", color= "Group") + scale_y_continuous(limits=c(0, 100)) + geom_col() + coord_flip()

```

```{r}
# Number of Students Experiencing Homelessness
table <- data %>% 
  group_by("Group" = suyi) %>%
  summarise(
    "n" = sum(as.numeric(homeless)),
    "Percent Homeless" = round((n/n())*100,2),
  )
kable(table, caption = "Students Experiencing Homelessness", col.names = c("Group", "Total", "Percent"))

data %>% 
  group_by(suyi) %>% 
  summarise(y = round((sum(homeless)/n())*100,2)) %>% 
  ggplot(aes(suyi,y, fill = suyi, fill = suyi)) + scale_fill_manual(values=c("black","#AA0000")) + labs(x = "", y = "Percent", color= "Group") + scale_y_continuous(limits=c(0, 100)) + geom_col() + coord_flip()
```

---

# Students Attendance 
A student is considered "chronically absent" when they miss 15 or more days of instruction in one academic school year. Chronic absenteeism can lead to student's missing important instructional time, ultimately causing students to fall behind in their academics. Furthermore, when students miss school they also miss important social interaction times that develop their interpersonal skills. 

According to this analysis, the average student in the Youth Initative Zone misses 12 days of instruction. High Schools students make up for the majority of the days missed, with New Futures Alternative, Cascade High School, and Olympic High School having the highest median of absenteeism. On the other hand, elementary school students account for the least amount of absences. Horizon, Franklin, and Valley Elementary have the lowest amount of students missing school. 

```{r}
table <- data %>% 
  group_by("Group" = suyi) %>%
  summarise(
    "Min" = min(days_absent),
    "Median" = median(days_absent),
    "Mean" = mean(days_absent),
    "Max" = max(days_absent))

kable(table, caption = "School Absenteeism") 

data %>% 
  ggplot(aes(reorder(school, days_absent, FUN = median), days_absent)) + geom_boxplot(fill = "grey90") + coord_flip() + labs(x = "School", y = "Days Absent")

```

```{r}
#Elementary Attendance 

table <- elem %>% 
  group_by("School" = school) %>%
  summarise(
    "Min" = min(days_absent),
    "Median" = median(days_absent),
    "Mean" = mean(days_absent),
    "Max" = max(days_absent))%>% 
  arrange(desc(Median))

kable(table, caption = "Elementary School Absenteeism") 

elem %>% 
  ggplot(aes(reorder(school, days_absent, FUN = median), days_absent)) + geom_boxplot(fill = "#4F95DB") + coord_flip() + labs(x = "School", y = "Days Absent")
```

```{r}
#Middle School Attendance 

table <- middle %>% 
  group_by("School" = school) %>%
  summarise(
    "Min" = min(days_absent),
    "Median" = median(days_absent),
    "Mean" = mean(days_absent),
    "Max" = max(days_absent))%>% 
  arrange(desc(Median))

kable(table, caption = "Middle School Absenteeism") 

middle %>% 
  ggplot(aes(reorder(school, days_absent, FUN = median), days_absent)) + geom_boxplot(fill = "#DBA14F") + coord_flip() + labs(x = "School", y = "Days Absent")
```

```{r}
#High School Attendance 

table <- hs %>% 
  group_by("School" = school) %>%
  summarise(
    "Min" = min(days_absent),
    "Median" = median(days_absent),
    "Mean" = mean(days_absent),
    "Max" = max(days_absent)) %>% 
  arrange(desc(Median))

kable(table, caption = "High School Absenteeism") 

hs %>% 
  ggplot(aes(reorder(school, days_absent, FUN = median), days_absent)) + geom_boxplot(fill = "#2ca25f") + coord_flip() + labs(x = "School", y = "Days Absent")
```

---

# RIT Scores 
```{r}
tresults <- t.test(df$fall_math ~ df$suyi)
tstar <- star(tresults$p.value)

table <- df %>% 
  group_by("Group" = suyi) %>%
  summarise(
    "Mean" = round(mean(fall_math, na.rm = TRUE),2),
    "Std. Err." = sd(fall_math, na.rm = TRUE)/sqrt(sum(!is.na(fall_math))),
    "t-test" = tstar
  )
kable(table, caption = "Fall Math Scores")

df %>% 
  group_by(suyi) %>% 
  summarise("mean" = mean(fall_math, na.rm = T)) %>% 
  ggplot(aes(suyi, mean, fill = suyi)) + scale_fill_manual(values=c("black","#AA0000")) + labs(x = NULL, y = "Average", fill= "Group") + geom_col() + coord_flip() #+ geom_text(aes(label = round(mean,2),y = mean + 0.05), position = position_dodge(0.9), vjust = 0)
```

```{r, warning=F}
#Average RIT Score by Semester
df_long %>% 
  ggplot(aes(subject, rit_score, fill= semester)) + scale_fill_manual(values=c("black", "grey","#AA0000")) + labs(title= "Average RIT Score by Semester" ,x = "Subject", y = "Average Score", fill= "Group") + geom_col(position = "dodge")  + scale_y_continuous(breaks = c(0,50,100,150,200,250,300))  + facet_wrap(~sex + suyi)
```

```{r, warning=F}
#Average RIT Score by Grade Level
df_long %>% 
  ggplot(aes(subject, rit_score, fill= semester)) + scale_fill_manual(values=c("black", "grey","#AA0000")) + labs(title= "Average RIT Score by Grade Level" ,subtitle = "elementary is grades K-5, middle is 6-8, and high school is 9-12", x = "Subject", y = "Average Score", fill= "Group") + geom_col(position = "dodge") + facet_wrap(~grade_level + suyi, nrow = 3) + scale_y_continuous(breaks = c(0,50,100,150,200,250,300))
```

```{r, warning=F}
#Average RIT Score by Race
df_long %>% 
  ggplot(aes(subject, rit_score, fill= semester)) + scale_fill_manual(values=c("black", "grey","#AA0000")) + labs(title= "Average RIT Score by Race" ,x = NULL, y = "Average Score", fill= "Group") + geom_col(position = "dodge") + facet_wrap(~race) + scale_y_continuous(breaks = c(0,50,100,150,200,250,300))
```

```{r, warning=F}
#Average RIT Score by Sex
df_long %>% 
  ggplot(aes(subject, rit_score, fill= semester)) + scale_fill_manual(values=c("black", "grey","#AA0000")) + labs(title= "Average RIT Score by Sex" ,x = NULL, y = "Average Score", fill= "Group") + geom_col(position = "dodge") + facet_wrap(~sex) + scale_y_continuous(breaks = c(0,50,100,150,200,250,300))
```

```{r, eval= FALSE}
#RIT Math Growth 
elem %>% 
  filter(!is.na(math_growth)) %>% 
  ggplot(aes(reorder(school, math_growth, FUN = median), math_growth, fill = school)) + geom_boxplot()  + labs(x = "School", y = "Math Growth") + coord_flip() + scale_fill_brewer(palette="RdBu")
 
```
 

```{r}
#Create smaller data frame for dumbbell viz

## Summarize Mean by School
mean_math <- df %>% 
  group_by(school, grade_level) %>% 
  summarise(mean_fall_math = mean(fall_math, na.rm = T),
            mean_spring_math = mean(spring_math, na.rm = T))

mean_read <- df %>% 
  group_by(school,grade_level) %>% 
  summarise(mean_fall_reading = mean(fall_reading, na.rm = T),
            mean_spring_reading = mean(spring_reading, na.rm = T))

## Turn summaries into a dataframe
mean_math <- as.data.frame(mean_math)
mean_read <- as.data.frame(mean_read)

## Create a Mean difference column 
mean_math <- mean_math %>% 
  mutate(mean_math_diff = round(mean_spring_math - mean_fall_math,2)) 

mean_read <- mean_read %>% 
  mutate(mean_reading_diff = round(mean_spring_reading - mean_fall_reading,2)) 
```
 
```{r}
# Create Mean_Read and Mean_Math datasets for each grade level 

## Math
elem_mean_math <- mean_math %>% filter(grade_level == "elementary") %>% arrange(desc(mean_math_diff))
middle_mean_math <- mean_math %>% filter(grade_level == "middle") %>% arrange(desc(mean_math_diff))
hs_mean_math <- mean_math %>% filter(grade_level == "high school") %>% arrange(desc(mean_math_diff))


## Reading 
elem_mean_reading <- mean_read %>% filter(grade_level == "elementary") %>% arrange(desc(mean_reading_diff))
middle_mean_reading <- mean_read %>% filter(grade_level == "middle") %>% arrange(desc(mean_reading_diff))
hs_mean_reading <- mean_read %>% filter(grade_level == "high school") %>% arrange(desc(mean_reading_diff))
```
 
```{r}
# Order School variable by mean reading difference variable

## Reading
elem_mean_reading$school <- fct_reorder(elem_mean_reading$school, elem_mean_reading$mean_reading_diff, max)

middle_mean_reading$school <- fct_reorder(middle_mean_reading$school, middle_mean_reading$mean_reading_diff, max)

hs_mean_reading$school <- fct_reorder(hs_mean_reading$school, hs_mean_reading$mean_reading_diff, max)


## Math
elem_mean_math$school <- fct_reorder(elem_mean_math$school, elem_mean_math$mean_math_diff, max)

middle_mean_math$school <- fct_reorder(middle_mean_math$school, middle_mean_math$mean_math_diff, max)

hs_mean_math$school <- fct_reorder(hs_mean_math$school, hs_mean_math$mean_math_diff, max)
```
 
 # Average RIT Elementary Schools Scored From Fall to Spring
 
```{r, warning = FALSE}
# Elementary Reading Dumbbell Plot 
ggplot(elem_mean_reading, aes(x=mean_fall_reading, xend=mean_spring_reading, y=school)) + geom_segment(aes(x=150, 
                         xend=250, 
                         y=school, 
                         yend=school), 
                     color="grey90", size=1)+
        geom_dumbbell(color="black", 
                      size_x=3.5, 
                      size_xend = 3.5,
                      colour_x="black", 
                      colour_xend = "#AA0000")+
        labs(x="Reading Score", y="School", 
             title="Elementary Fall to Spring Average RIT Reading Scores", 
             caption="2014 School year") +
    geom_text(data=filter(elem_mean_reading, school == "Valley Elementary"), aes(x=mean_fall_reading, y=school, label="Fall"),
          color="black", size=2.75, vjust=-2.5, position = position_dodge(width = 2)) +
geom_text(data=filter(elem_mean_reading, school == "Valley Elementary"), color="#AA0000", size=2.75, vjust=-2.5,
          aes(x=mean_spring_reading, y=school, label="Spring"), position = position_dodge(width = 2)) +
  geom_text(data=elem_mean_reading, aes(x=mean_fall_reading, y=school, label=round(mean_fall_reading,2)),
          color="black", size=2.75, vjust=2.5, position = position_dodge(width = 2)) +
geom_text(data=elem_mean_reading, color="black", size=2.75, vjust=2.5,
          aes(x=mean_spring_reading, y=school, label=round(mean_spring_reading,2)), position = position_dodge(width = 2)) +
  geom_rect(data=elem_mean_reading, aes(xmin=230, xmax=250, ymin=-Inf, ymax=Inf), fill="grey90") +
geom_text(data=elem_mean_reading, aes(label=paste0(round(mean_reading_diff,2)), y=school, x=240), fontface="bold", size=3) +
geom_text(data= filter(elem_mean_reading, school == "Valley Elementary"), 
            aes(x=240, y=school, label="Difference"),
            color="black", size=3.1, vjust=-3, fontface="bold") + scale_x_continuous(expand=c(0,0), limits=c(150, 250)) + scale_y_discrete(expand=c(0.2,0))
```
 
```{r}
#Middle Reading Dumbbell Plot 
ggplot(middle_mean_reading, aes(x=mean_fall_reading, xend=mean_spring_reading, y=school)) + geom_segment(aes(x=150, 
                         xend=250, 
                         y=school, 
                         yend=school), 
                     color="grey90", size=1)+
        geom_dumbbell(color="black", 
                      size_x=3.5, 
                      size_xend = 3.5,
                      colour_x="black", 
                      colour_xend = "#AA0000")+
        labs(x="Reading Score", y="School", 
             title="Middle School Fall to Spring Average RIT Reading Scores", 
             caption="2014 School year") +
    geom_text(data=filter(middle_mean_reading, school == "Sound View Middle School"), aes(x=mean_fall_reading, y=school, label="Fall"),
          color="black", size=2.75, vjust=-2.5, position = position_dodge(width = .5)) +
geom_text(data=filter(middle_mean_reading, school == "Sound View Middle School"), color="#AA0000", size=2.75, vjust=-2.5,
          aes(x=mean_spring_reading, y=school, label="Spring"), position = position_dodge(width = 2)) +
  geom_text(data=middle_mean_reading, aes(x=mean_fall_reading, y=school, label=round(mean_fall_reading,2)),
          color="black", size=2.75, vjust=2.5, position = position_dodge(width = .5)) +
geom_text(data=middle_mean_reading, color="black", size=2.75, vjust=-1,
          aes(x=mean_spring_reading, y=school, label=round(mean_spring_reading,2)), position = position_dodge(width = 5)) +
  geom_rect(data=middle_mean_reading, aes(xmin=230, xmax=250, ymin=-Inf, ymax=Inf), fill="grey90") +
geom_text(data=middle_mean_reading, aes(label=paste0(round(mean_reading_diff,2)), y=school, x=240), fontface="bold", size=3) +
geom_text(data= filter(middle_mean_reading, school == "Sound View Middle School"), 
            aes(x=240, y=school, label="Difference"),
            color="black", size=3.1, vjust=-3, fontface="bold") + scale_x_continuous(expand=c(0,0), limits=c(150, 250)) + scale_y_discrete(expand=c(0.2,0))
```
 
 
```{r}
#High School Reading Dumbbell Plot 
ggplot(hs_mean_reading, aes(x=mean_fall_reading, xend=mean_spring_reading, y=school)) + geom_segment(aes(x=150, 
                         xend=250, 
                         y=school, 
                         yend=school), 
                     color="grey90", size=1)+
        geom_dumbbell(color="black", 
                      size_x=3.5, 
                      size_xend = 3.5,
                      colour_x="black", 
                      colour_xend = "#AA0000")+
        labs(x="Reading Score", y="School", 
             title="High School Fall to Spring Average RIT Reading Scores", 
             caption="2014 School year") +
    geom_text(data=filter(hs_mean_reading, school == "Olympic High School"), aes(x=mean_fall_reading, y=school, label="Fall"),
          color="black", size=2.75, vjust=-2.5, position = position_dodge(width = 2)) +
geom_text(data=filter(hs_mean_reading, school == "Olympic High School"), color="#AA0000", size=2.75, vjust=-2.5,
          aes(x=mean_spring_reading, y=school, label="Spring"), position = position_dodge(width = 2)) +
  geom_text(data=hs_mean_reading, aes(x=mean_fall_reading, y=school, label=round(mean_fall_reading,2)),
          color="black", size=2.75, vjust=2.5, position = position_dodge(width=.5)) +
geom_text(data=hs_mean_reading, color="black", size=2.75, vjust=-1,
          aes(x=mean_spring_reading, y=school, label=round(mean_spring_reading,2)), position = position_dodge(width=1)) +
  geom_rect(data=hs_mean_reading, aes(xmin=230, xmax=250, ymin=-Inf, ymax=Inf), fill="grey90") +
geom_text(data=hs_mean_reading, aes(label=paste0(round(mean_reading_diff,2)), y=school, x=240), fontface="bold", size=3) +
geom_text(data= filter(hs_mean_reading, school == "Olympic High School"), 
            aes(x=240, y=school, label="Difference"),
            color="black", size=3.1, vjust=-3, fontface="bold") + scale_x_continuous(expand=c(0,0), limits=c(150, 250)) + scale_y_discrete(expand=c(0.2,0))
```
 
 
 
 
-Make tables to accompany each graph made 
- Find out what the national rit score is and then graph a line on the graph showing where SUYI fall within that range
- Write up a summary of the findings 


